pema application

### 2022-11-19 paper/action_letter.Rmd
update 2022-11-19 10:59:30

```{r, message=FALSE, warning=FALSE}
library(revise)
man <- read_manuscript("manuscript.Rmd")
```

@@

`r get_manuscript("lassoabstract")`

@@

@@

\RC{The introduction is too long in terms of explanation of the meta-regression and selection of covariates problems, with many repetitions. For example, end of page 4 and beginning of page 5 include many repetitions about between-study heterogeneity. Other parts, instead, require a substantially deeper explanation. }

@@

\RC{Probably, in (1) you mean \theta and not \Theta? As you have \theta int the text. Why do you use theta and not beta, as you do for the meta-regression model in (7)? The notation would be simplified and would be more consistent.}

@@

@@

@@

@@

>>>>

```{r, message=FALSE, warning=FALSE}
library(revise)
read_manuscript("manuscript.Rmd")
```

@@

`r get_revision("lassoabstract")`

@@

We see now that we did not report clearly enough how many design factors there were and what they were.
Apparently, it was also not sufficiently clear that "noise moderators" are not the same as "design factors".
To address this comment and avoid confusion, we have rewritten this paragraph as follows:

`r get_revision("designfactors")`

@@

We thank the Reviewer for their constructive comments, which substantially helped improve the quality of the manuscript.
We have tried to address them all in turn, as detailed below.

\RC{The introduction is too long in terms of explanation of the meta-regression and selection of covariates problems, with many repetitions. For example, end of page 4 and beginning of page 5 include many repetitions about between-study heterogeneity. Other parts, instead, require a substantially deeper explanation.}

@@

\RC{Probably, in (1) you mean $\theta$ and not $\Theta$? As you have $\theta$ int the text. Why do you use theta and not beta, as you do for the meta-regression model in (7)? The notation would be simplified and would be more consistent.}

@@

We have made the suggested change.

@@

We thank the Reviewer for suggesting these references, which had eluded our literature search.

We agree that the use of weakly informative priors for heterogeneity parameters was insufficiently discussed in the previous version of our manuscript, and have now added a paragraph on that topic (see our response to the next comment).

However, it is important to note that the use of weakly informative priors (WIP) for heterogeneity parameters serves a categorically different purpose than the use of regularizing priors for regression coefficients - even if the term "regularization" has been used for both in prior literature.
The purpose of WIP for heterogeneity parameters is to aid model convergence and avoid boundary estimates.
The purpose of regularizing priors for regression coefficients is to perform variable selection.
We believe that the newly added paragraph sufficiently clarifies these distinct uses of "regularization" (see response to next comment).

Thank you for pointing out these relevant references. We have included the reference to Chung et al. (2013), Gelman (2006) and Rover et al. (2021) in the new section on the prior for $\tau$ (see the next comment). In addition we have added the following section on page ... to be more explicit about the terminology of different types of priors:

Suggest to add this paragraph in the section on Bayesian estimation after "which reflects expectations about likely parameter values after having seen the data." Note: if included, this should be updated in the text from a previous comment to reviewer 1 as well. Also here it is relevant whether we use "regularizing" or "shrinkage" priors and should mention the definite choice explicitly.

"As a result, the posterior distribution is a compromise between the likelihood of the data and the prior distribution. The influence of either the data or the prior is determined by the sample size as well as the informativeness of the prior distribution. The larger the sample size, the more influential the likelihood of the data will be. Similarly, as the prior distribution becomes more informative, i.e., more peaked, it will exert more influence on the results. Priors can thus be placed on a continuum from "non-informative" to "highly informative". Weakly informative or regularizing priors are often used in situations when there is some prior information available, for example regarding the boundaries of the parameter space or, as is the case here, regarding the existence of parameters equal to zero. Throughout this manuscript, we will use the term "shrinkage prior" to refer to the weakly informative or regularizing prior that holds the prior knowledge that some coefficients are equal to zero and should therefore be shrunken towards zero."

@@

We agree with the Reviewer that the prior specification for the heterogeneity parameter $tau$ is important and should be addressed in the text.
To address this comment, we have included the following paragraph in the revision:

`r get_revision("tauprior")`

Chung Y, Rabe-Hesketh S, Choi IH. Avoiding zero between-study variance estimates in random-effects meta-analysis. Stat Med. 2013;32(23):4071-4089.

Gelman A. Prior distributions for variance parameters in hierarchical models. Bayesian Anal. 2006;1(3):515-534. [https://doi.org/10.1214/06-BA117A](https://doi.org/10.1214/06-BA117A "https://doi.org/10.1214/06-BA117A").

Gronau, Q. F., Van Erp, S., Heck, D. W., Cesario, J., Jonas, K. J., & Wagenmakers, E. J. (2017). A Bayesian model-averaged meta-analysis of the power pose effect with informed and default priors: The case of felt power. _Comprehensive Results in Social Psychology_, _2_(1), 123-138.

Röver, C, Bender, R, Dias, S, et al. On weakly informative prior distributions for the heterogeneity parameter in Bayesian random-effects meta-analysis. Res Syn Meth. 2021; 12: 448– 474. [https://doi.org/10.1002/jrsm.1475](https://doi.org/10.1002/jrsm.1475 "https://doi.org/10.1002/jrsm.1475")

@@

We have made the suggested correction. Both in the Abstract and in the text, the first time we introduce RMA, we introduce it as "random effects meta-analysis using restricted maximum likelihood".
